
%\documentclass{elsart}               % The use of LaTeX2e is preferred.

\documentclass[twocolumn]{autart}    % Enable this line and disable the 
                                     % preceding line to obtain a two-column 
                                     % document whose style resembles the
                                     % printed Automatica style.


\usepackage{graphicx}          % Include this line if your 
                               % document contains figures,
%\usepackage[dvips]{epsfig}    % or this line, depending on which
                               % you prefer.

\include{settings}
\begin{document}

\begin{frontmatter}
\runtitle{Selective Harmonic Elimination via Optimal Control}   % Running title for regular 
                                              % papers but only if the title  
                                              % is over 5 words. Running title 
                                              % is not shown in output.

\title{Selective Harmonic Elimination via Optimal Control} % Title, preferably not more 
                                                 % than 10 words.

\thanks[footnoteinfo]{This paper was not presented at any IFAC 
meeting.}

\author[FD,UD]{Umberto Biccari}\ead{umberto.biccari@deusto.es},    % Add the 
\author[UAM,FD]{Carlos Esteve}\ead{carlos.esteve@uam.es},               % e-mail address 
\author[UD]{Jes\'us Oroya}\ead{djoroya@deusto.es}  % (ead) as shown
\address[FD]{Chair of Computational Mathematics, Fundaci\'on Deusto, Avenida de las Universidades 24, 48007 Bilbao, Basque Country, Spain.}  %
\address[UD]{Universidad de Deusto, Avenida de las Universidades 24, 48007 Bilbao, Basque Country, Spain.}  %
\address[UAM]{Departamento de Matem\'aticas, Universidad Aut\'onoma de Madrid, 28049 Madrid, Spain.}  % Please supply                                              

          
\begin{keyword}                           % Five to ten keywords,  
Selective Harmonic Elimination; Finite Set Control, Piecewise Linear function.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard


\begin{abstract}                          % Abstract of not more than 200 words.
El problema de \emph{Selective Harmonic Elimination pulse-width modulation}(SHE) es planteado como el problema de control óptimo, con el fin de encontrar soluciones de ondas escalón sin prefijar el número de ángulos de conmutación. De esta manera, la metodología de control óptimo es capaz de encontar la forma de onda óptima y de encontrar la localizaciones de los ángulos de conmutación, incluso sin prefijar el número de conmutaciones. Este es un nuevo enfoque para el problema SHE en concreto y para los sistemas de control con un conjunto finito de controles admisibles en general.

\end{abstract}

\end{frontmatter}

\input{contens/P01-Indroduction}
\input{contens/P02-RelatedWork}
\input{contens/P03-SHE-as-system}
\input{contens/P04-Problem-Statement}
\input{contens/P06-NumericalResults}
\input{contens/P07-Conclusions}

\begin{ack}                               % Place acknowledgements
Partially supported by the Roman Senate.  % here.
\end{ack}
 
\bibliographystyle{apalike}        % Include this if you use bibtex 
\bibliography{bib}           % and a bib file to produce the 
                                 % bibliography (preferred). The
                                 % correct style is generated by
                                 % Elsevier at the time of printing.




\end{document}